Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-06-06 meta_analysis_sexual_selection_pop_fitness.Rmd
6/6 Update

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools) 
source("Vdodge_function.R") # nice function for ggplot
```

```{r echo=FALSE, results='hide'}
library(knitr) # set up cacheing to save time when re-building the html document
```
`r opts_chunk$set(cache=TRUE)`

@@

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.We obtained the journal impact factor for each effect size at the time of publication using InCites Journal Citation Reports.
<br></br>

@@

Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
```
<br></br>

@@

```{r, fig.height=18, fig.width=12}

# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
prelim.data$Outcome_f = factor(prelim.data$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

@@

library(ggthemes)
#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%

@@

  scale_color_brewer(name = "Relationship\nto fitness", 
                    palette = "Set1", 
                    breaks=c("Ambiguous","Indirect","Direct"))+

@@

  scale_fill_brewer(name = "Relationship\nto fitness", 
                    palette = "Set1", 
                    breaks=c("Ambiguous","Indirect","Direct"))+

@@

  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20")))+

@@

ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)
p.meta

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

@@

**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3 (fix this).

```{r, warning = FALSE}
outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
                          mods = ~ 1, 
                          method = "REML",
                          random = ~ 1 + Study.ID,
                          subset = (Outcome_f == x),
                          data = prelim.data))

@@

simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
# simple.frame$vi <- as.matrix(simple.frame$vi)
# simple.frame$W <- diag(1/(simple.frame$vi))
# 
# XO <- model.matrix(model.complete2)
# PO <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
# 100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))

#I couldn't get mapply to work when calculating I2 so I calculated them manually.

@@

outcome.frame %>% pander(split.cell = 40, split.table = Inf)

#Can't get the llply or mapply to work on the list of outcomes

# I2df <- llply(outcome.models, function(x) {
#   prelim.data %>% filter(prelim.data$Outcome == outcome.list)
# })
#   #Run estimate of heterogeneity
# Wlist <- llply(outcome.list, function(x) {diag(1/I2df[[x]]$var.g)}) #X
# 
# Xlist <- llply(outcome.list, function(x) {model.matrix(outcome.models[[x]])}) #Y
# 
# Pfunc <- Map(function(X,Y,Z) {
#   X[[Z]] - X[[Z]] %*% Y[[Z]] %*% solve(t(Y[[Z]]) %*% X[[Z]] %*% Y[[Z]]) %*% t(Y[[Z]]) %*% X[[Z]]},
#   X=Wlist, Y=Xlist, Z=1:19)
# 
# llply()
# 
# I2list <- llply(outcome.list, function(x) {100 * sum(outcome.models[[x]]$sigma2) / (sum(outcome.models[[x]]$sigma2) + (outcome.models[[x]]$k-outcome.models[[x]]$p)/sum(diag(Wlist - Wlist %*% Xlist %*% solve(t(Xlist) %*% Wlist %*% Xlist) %*% t(Xlist) %*% x)))})
# 
# matrix(outcome.list)
```

___________________

@@

summary(model.preliminary)

#Also use bayesian model

brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding 
                + (1|Study.ID) #group level effect #1
                + (1|Outcome)
                + (1|Taxon), 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = prelim.data %>% mutate(SE = sqrt(var.g)))

#Plot model results
prelim.results.bayesplot <- bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + 
  geom_vline(xintercept = 0, linetype = 2)

@@

From this model we can see that there are several redundant moderators: Blinding, Generations and the Outcome class (direct, indirect and ambiguous) show little effect and are not key to our research question (like sex and environment are). However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate this fixed effect further...

__________________________________

@@

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding). In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.

<input type=button class=hideshow></input>
```{r, warning=FALSE}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

@@

model.complete <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = restricted.data)

summary(model.complete)

#Have taxon as fixed effects
brms.complete <- brm(g | se(SE)  ~ 1 + Sex * Environment + Taxon
                + (1|Study.ID) #group level effect #1
                + (1|Outcome), #group level effect #2 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = restricted.data %>% mutate(SE = sqrt(var.g)))

bayesplot::mcmc_areas(posterior_samples(brms.complete)[,1:13]) +
  geom_vline(xintercept = 0, linetype = 2)

# new.data <- restricted.data %>% 
#   mutate(SE = sqrt(var.g)) %>% 
#   select(Sex, Environment, Blinding, Generations, SE, Taxon) %>% 
#   mutate(Generations = mean(log(Generations)), 
#          Blinding = "Blind", 
#          Taxon = "Fly",
#          Outcome = "Reproductive Success",
#          SE = 0) %>% 
#   distinct() %>% arrange(Sex, Environment)
# predictions.complete <- data.frame(new.data, fitted(brms.complete, newdata = new.data, re_formula = NA))
# 
# pd <- position_dodge(0.2)
# predictions.complete %>% ggplot(aes(Sex, Estimate, group = Environment, colour = Environment)) + 
#   geom_errorbar(aes(ymin = X2.5.ile, ymax = X97.5.ile), position = pd, width = 0) +
#   geom_point(position = pd) +
#   coord_flip()
```

The result is a model with estimates for various taxa, species, sexes and environments. To make sense of these estimates we should obtain average predictions for each moderator variable class of interest. We can do that by using a modified version version of a function used by Holman 2017. Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc. This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
```{r, warning=FALSE}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[3] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

@@

predictions.complete <- left_join(predictions.complete, countpred, by = c("Sex", "Environment", "Taxon"))
```

Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.

<!-- > I would like to know how to join a table with mean, and CI values to the forest plots I am generating. -->

<!-- > You can make tables with ggplot, and bind them to graphs using the grid and gridExtra packages. It's pretty hard! See ?gridExtra::tableGrob.  -->
<!-- > Honestly might be easier to do it manually with e.g. Inkscape or Illustrator.	 -->

```{r, fig.height= 6, fig.width=8}
pd <- position_dodgev(0.5)

Taxon.metaanlysis <- predictions.complete %>% 
    mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=2, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-1, 2)+
  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T))+
    theme_bw()+

@@

ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 6, width = 8)
Taxon.metaanlysis
```
<br></br>
**Figure S2:** The predictions from this model indicate some heterogeneity between taxon. However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size. As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands. Importantly, the overall direction of effect does not change between taxon, although guppies and mice show near zero effect sizes. Here we see that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.

**Table S7** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.

@@

@@

Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than unstressed environments? **AND** Do the benefits of sexual selection accrue more for female fitness components?

We run a three level model where the outcome is nested within a study (Study.ID). Other potential random effects include Species and Group.ID. However the estimate (variance from random effect) of these two other potential random effects tended towards zero and were dropped from the model. Additionally the model could be run with just Study.ID, but from our exploration of heterogeneity (below) we see that there is sufficient correlation (but not ICC = 1) between outcomes to include it as a random effect within the model.

```{r}
#run model without taxon: same random effects as above
model.complete2 <- rma.mv(g, var.g, 
                          mods = ~ 1 + Sex * Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                          method = "REML", 
                          data = restricted.data)
summary(model.complete2)
```
<br></br>

Now plot the model predictions using a similar function to the one used in the above section with taxon.

```{r, fig.height= 6, fig.width=6}

#Generate predictions without taxon utilising the previously described function

@@

predictions.complete2 <- left_join(predictions.complete2, countpred, by = c("Sex", "Environment"))

>>>>

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(car)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
library(ggridges)
library(rstan) #Note that installation requires some effort: dependency for brms
library(brms) 
library(backports) #seems to be a dependency
library(bayesplot)
#devtools::install_github("mvuorre/brmstools")
library(brmstools) 
source("Vdodge_function.R") # nice function for ggplot
source("Tidy_functions_for_brms.R") #Tidy functions for making model tables for brms
```

```{r echo=FALSE, results='hide', warning=FALSE}
library(knitr) # set up cacheing to save time when re-building the html document
```
`r opts_chunk$set(cache=TRUE)`

@@

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.We obtained the journal impact factor for each effect size at the time of publication using InCites Journal Citation Reports.

_________

@@

Outcome_and_sex %>% pander(split.cell = 40, split.table = Inf)
```

@@

```{r, fig.height=18, fig.width=12}
# Create new factor to order factors in a way where Ambig, Indirect and Direct are Grouped
prelim.data$Outcome_f = factor(prelim.data$Outcome, levels = c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))

@@

library(ggthemes)
#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Outcome.Class = factor(Outcome.Class, levels = c("Ambiguous", "Indirect", "Direct"))) %>%

@@

  scale_color_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                    name = "Relationship\nto fitness")+

@@

  scale_fill_manual(values = c("Ambiguous" = "#a50f15", "Indirect" = "#fe9929", "Direct" = "#4daf4a"), 
                    name = "Relationship\nto fitness")+

@@

  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20", size = 6)),
         shape = guide_legend(override.aes = list(size = 4.5)))+

@@

p.meta

### We can save the file in several vector graphics forms

#ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
# 
# pdf("figures/Big_forest_plot.pdf", width=12, height=18)
# p.meta
# dev.off()
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to measured fitness components and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

___________

@@

**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3. 
<input type=button class=hideshow></input>
```{r, warning = FALSE}
outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
                          mods = ~ 1, 
                          method = "REML",
                          random = ~ 1 + Study.ID,
                          subset = (Outcome_f == x),
                          data = prelim.data))

@@

simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))

#There is no simple way to get I2 for multilevel models in metafor, so we can obtain them manually for each outcome

@@

#Only present subset model results for outcomes with 4 or more effect sizes

outcome.frame %>% filter(Outcome != "Behavioural Plasticity" & Outcome != "Pesticide Resistance" & Outcome != "Strength") %>% pander(split.cell = 40, split.table = Inf)
```

@@

summary(model.preliminary, digits = 2)

Here we can also run a bayesian model alongside the restricted maximum likelihood model (metafor)
```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
#Also use bayesian model
brms.preliminary <- brm(g | se(SE)  ~ 1 + Sex * Environment + log(Generations) + Blinding #Note that running se(SE, sigma = TRUE) gives different result due to a difference in priors
                + (1|Study.ID) #group level effects
                + (1|Outcome)
                + (1|Taxon), 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, #Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.999, max_treedepth = 15),
                data = prelim.data %>% mutate(SE = sqrt(var.g)))

```{r}
#Plot model results
prelim.results.bayesplot <- bayesplot::mcmc_areas(posterior_samples(brms.preliminary)[,1:11]) + 
  geom_vline(xintercept = 0, linetype = 2) +

@@

make_text_summary(brms.preliminary) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
```
**Figure S2 & Table S7:** Bayesian model results for a preliminary model that explores many covariates collected in the dataset.

From these models we can see that there are several redundant moderators: Blinding and Generations show little effect and are not key to our research question (like sex and environment are). However, because taxa is a likely source of heterogeneity and effect size could reasonably be expected to differ between taxa, we investigate taxa as a fixed effect.

@@

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding). In this model we use Sex, Environment, Taxon and the interaction between sex and environment.

<input type=button class=hideshow></input>
```{r, results='hide', message=FALSE, error = FALSE, warning=FALSE}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

@@

model.complete <- rma.mv(g, V = var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = restricted.data)

summary(model.complete, digits = 2)
```

The result is a model with estimates for various taxa, species, sexes and environments. To make sense of these estimates we should obtain average predictions for each moderator variable class of interest. We can do that by using a modified version version of a function used by Holman 2017. Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc. This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
```{r, warning=FALSE, fig.height= 8, fig.width=8}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[3] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

@@

#Thirdly, plot the model predictions for effect size (Hedges' g) for male, female and both sexes under both stressed and unstressed condition and faceted for each taxon.

pd <- position_dodgev(0.6)

Taxon.metaanlysis <- predictions.complete %>% 
    mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
         Sex = factor(Sex, levels = c("Male", "Both", "Female"))) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "black") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=2, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-1, 2)+
  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
  scale_fill_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  scale_color_manual(values = c("Male" = "#e41a1c", "Female" = "#377eb8", "Both" = "#4daf4a"))+
  guides(fill = guide_legend(reverse=T, override.aes = list(size = 4.5)))+

@@

#ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.svg", height = 8, width = 8)
Taxon.metaanlysis
```
<br></br>
**Figure S3:** The predictions from this model indicate some heterogeneity between taxon. However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size. As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands. Importantly, the overall direction of effect does not change between taxon, although guppies and mice show near zero effect sizes. Here we see that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.

**Table S8** The predictions for the above figure looking at the effect of sexual selection amongst taxa uses the following dataframe.

@@

Given that none of categories of taxa significantly impact effect size we can incorporate them as random/group level effects in later models.

@@

Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than benign environments? **AND** Do the benefits of sexual selection differ between the sexes?

We can run a model where the outcome is crossed with study (Study.ID) and Taxon as random effects and environment, sex and their interactions are fized effects.

```{r}
#run model with taxon as a random effect
model.complete2 <- rma.mv(g, V = var.g, 
                          mods = ~ 1 + Sex * Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome,
                                       ~ 1 | Taxon), 
                          method = "REML", 
                          data = restricted.data)
summary(model.complete2, digits = 2)
```

####Comparisons of environment and Sex Conditions REML model through anovas

**Table S9** Using the ``anova.rma`` function we can conduct hypothesis tests between two categorical groups in the model. Here we conduct 5 tests testing relative effects of sexual selection between the sexes and in different environments.

```{r}
#anova where you specify the values based on the list of moderators
anova.1 = anova(model.complete2, L=c(1, 0, -1, 0, 0, 0)) 
anova.2 = anova(model.complete2, L=c(0, 0, 0, 1, 0, -1))
anova.3 = anova(model.complete2, L=c(0, 0, 1, 0, 0, -1))
anova.4 = anova(model.complete2, L=c(1, 0, 0, -1, 0, 0))
anova.5 = anova(model.complete2, L=c(0, 1, 0, 0, -1, 0))

anova.list <- list(anova.1, anova.2, anova.3, anova.4, anova.5)

anova.frame <- t(data.frame(lapply(anova.list, function(x) {
  data.frame(x[["hyp"]],
  x[["Lb"]],
  x[["se"]],
  x[["Lb"]] - 1.96*x[["se"]],
  x[["Lb"]] + 1.96*x[["se"]],
  x[["pval"]])
})))
anova.frame <- as.data.frame(split(anova.frame, rep(1:6)))
colnames(anova.frame) <- c("Hypothesis", "Estimate", "Est.Error", "CI.Lower", "CI.Upper", "pval")
anova.frame$Estimate <- as.numeric(levels(anova.frame$Estimate))[anova.frame$Estimate]
anova.frame$Est.Error <- as.numeric(levels(anova.frame$Est.Error))[anova.frame$Est.Error]
anova.frame$CI.Lower <- as.numeric(levels(anova.frame$CI.Lower))[anova.frame$CI.Lower]
anova.frame$CI.Upper <- as.numeric(levels(anova.frame$CI.Upper))[anova.frame$CI.Upper]
anova.frame$pval <- as.numeric(levels(anova.frame$pval))[anova.frame$pval]
anova.frame <- format(anova.frame, digits = 2)
anova.frame$star <- c("", "*", "*", "*", "")
colnames(anova.frame)[colnames(anova.frame)=="star"] <- " "
anova.frame$pval <- NULL
anova.frame %>% pander(split.table = Inf)
```
<br></br>
From these anovas we see that a stressful environment leads to a significantly greater increase in fitness components for "female"" but NOT "both" sexes, while significantly decreasing male fitness. We can also test if there is a difference between males and females in stressful but not benign conditions.

###Bayesian model on the effects of environment and sex

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. The ``brms`` package sets standard priors that are selected to be 'weakly informative'. The _R^2^_ of this Bayesian model was 0.35 (95% CIs = 0.31-0.39).
```{r, warning = FALSE, results='hide', message=FALSE, error = FALSE}
#Use brms to create a model similar to the one used in the REML approach. 
brms.complete2 <- brm(g | se(SE)  ~ 1 + Sex * Environment #se(SE, sigma = TRUE) gives differnt results
                + (1|Taxon) #group level effect #1
                + (1|Study.ID) #group level effect #2
                + (1|Outcome), #group level effect #3 
                family = "gaussian", 
                seed = 1,
                cores = 4, chains = 4, iter = 4000, # Run 4 chains in parallel for 4000 iterations (2000 are burn in)
                control = list(adapt_delta = 0.9999, max_treedepth = 15),
                data = restricted.data %>% mutate(SE = sqrt(var.g)))

```
<br></br>
We can then get the distribution of posterior fitted values and examine the model summary

**Table S10** Model estimate summary table for the Bayesian model investigating the effect of environment and sex (alongside sexual selection) on fitness. 
```{r}
#You can obtain a posterior sampling through the ``fitted.brmsfit`` function, which gives the same posterior values as doing it manually (see below).**Note that the fitted values obtained here have much smaller error than the predict values**

#Expand grid for environment and sex
# brms.newdata <- as.data.frame(expand.grid(Sex = c("M", "B", "F"),
#                            Environment = c("Unstressed", "Stressed")))
# #Add variance
# brms.newdata$var.g <- av.var.g
# 
# #Add predictions
# brms.predict <- fitted(meta.brms, newdata = brms.newdata, re_formula = NA)
# brms.predict <- as.data.frame(brms.predict)
# brms.predictions <- data.frame(brms.newdata$Sex, brms.newdata$Environment, brms.predict$Estimate, brms.predict$Est.Error, brms.predict$Q2.5, brms.predict$Q97.5)
# 
# #Name columns
# colnames(brms.predictions) <- c("Sex", "Environment", "Estimate", "Error", "LCI", "UCI")

post <- (posterior_samples(brms.complete2, 
                           pars = c("b_Intercept", "b_SexB", "b_SexF", 
                                    "b_EnvironmentStressed", "b_SexB:EnvironmentStressed", 
                                    "b_SexF:EnvironmentStressed")) %>%
         mutate(both_benign = b_Intercept + b_SexB,
         both_stressful = b_Intercept + b_SexB + b_EnvironmentStressed + `b_SexB:EnvironmentStressed`,
         male_benign = b_Intercept,
         male_stressful = b_Intercept + b_EnvironmentStressed,
         female_benign = b_Intercept + b_SexF,
         female_stressful = b_Intercept + b_SexF + b_EnvironmentStressed + `b_SexF:EnvironmentStressed`))[,-(1:6)]

#Clean up dataframe
post <- melt(post, id = c("Sex", "Environment"))
post$variable <- NULL

make_text_summary(brms.complete2) %>% add_significance_stars() %>% tibble::rownames_to_column("Model Parameter") %>% pander()
```
<br></br>
Like with the REML approach, from these model results we can test several hypotheses between the categories of environment and sex. For instance, the first hypothesis in the table below tests whether there is a difference between male and female fitness increase under sexual selection in benign conditions. With the answer stating that they largely overlap in their predictions and are the same, to 95 % confidence.

**Table S11** Hypothesis tests for the Bayesian model are similar to the REML model (Table S9), with slight differences to CIs.
```{r}
#Obtain hypothesis estimates
brms.hypothesis <- hypothesis(brms.complete2, c("Intercept = SexF",
                             "EnvironmentStressed = SexF:EnvironmentStressed",
                             "SexF = SexF:EnvironmentStressed",
                             "Intercept = EnvironmentStressed",
                             "SexB = SexB:EnvironmentStressed"))
#Format into dataframe
brms.hypothesis.table <- 
  data.frame(brms.hypothesis[["hypothesis"]][["Hypothesis"]],
             brms.hypothesis[["hypothesis"]][["Estimate"]],
             brms.hypothesis[["hypothesis"]][["Est.Error"]],
             brms.hypothesis[["hypothesis"]][["CI.Lower"]],
             brms.hypothesis[["hypothesis"]][["CI.Upper"]],
             brms.hypothesis[["hypothesis"]][["Star"]])
colnames(brms.hypothesis.table) <- c("Hypothesis", "Estimate", "Est.Error", "CI.Lower", "CI.Upper", " ")
brms.hypothesis.table <- format(brms.hypothesis.table, digits = 2)
brms.hypothesis.table %>% pander(split.table = Inf)
```
<br></br>
Using predictions from both REML and Bayesian models we can obtain a figure that plots the mean/median predictions as well as distribution density (Bayesian) and 95 % CI (REML).

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, error = FALSE}
#Generate predictions without taxon utilising the previously described function

@@

predictions.complete2 <- left_join(predictions.complete2, countpred, by = c("Sex", "Environment"))
colnames(predictions.complete2) <- c("Sex", "Environment", "Prediction", "SE", "CI.lb", "CI.ub", "n")
predictions.complete2 <- predictions.complete2 %>%
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female"),
         Environment = replace(as.character(Environment), Environment == "Stressed", "Stressful"),
         Environment = replace(Environment, Environment == "Unstressed", "Benign"),
         Sex = factor(Sex, levels = c("Male", "Both", "Female")))
